\let\nofiles\relax

\documentclass[margin,line]{res}

\input{settings.tex}

\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{lastpage}

\newcommand{\MONTH}{%
  \ifcase\the\month
  \or Jan% 1
  \or Feb% 2
  \or Mar% 3
  \or Apr% 4
  \or May% 5
  \or Jun% 6
  \or Jul% 7
  \or Aug% 8
  \or Sep% 9
  \or Oct% 10
  \or Nov% 11
  \or Dec% 12
  \fi}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot[C]{~\\~\\ \hfill \footnotesize Page \thepage~of~\pageref{LastPage} \hfill Revised \MONTH~\the\year}

\renewcommand{\headrulewidth}{0pt}

\xdefinecolor{darkBlue}{rgb}{0.102, 0.235, 0.447}
\xdefinecolor{lightBlue}{rgb}{0.169, 0.38, 0.702}

\usepackage[colorlinks=false,pdfborder={0 0 0},urlcolor= lightBlue,colorlinks=true,linkcolor=black]{hyperref}


\begin{document}

\name{Colin Rundel \hspace{7.1cm} {\small \href{mailto:rundel@gmail.com}{rundel@gmail.com} / \href{mailto:colin.rundel@duke.edu}{colin.rundel@duke.edu}}}
\address{
204 Old Chemistry Building $\bullet$ Dept of Statistical Science, Duke University  
}

\begin{resume}

%

\vspace{3mm}

\section{\sc Research Interests}
Applied spatial statistics with a focus on biological and ecological systems, Bayesian statistics, computational methods, statistics and computing education and pedagogy.

\vspace{4mm}

%

\section{\sc Education}
University of California, Los Angeles, Department of Statistics
\vspace{1mm}
\begin{list1}
\item[] Ph.D. in Statistics,  2012
\item[] M.S. in Statistics,  2008
\vspace{1mm}
\item[] Dissertation Topic:  Bayesian Methods for Spatial Assignment of Migratory Birds
\item[] Advisors:  Jan de Leeuw and John Novembre
\end{list1}

\vspace{-0.13cm}
California Institute of Technology
\vspace{1mm}
\begin{list1}
\item[] B.S. in Biology, 2003
\end{list1}

\vspace{3mm}

%

\section{\sc Employment}

Assistant Professor of the Practice \hfill June 2015 - Present \\
{Department of Statistical Science}, Duke University \\
\vspace{-0.5cm}

Lecturer in Statistics and Data Science \hfill May 2019 - May 2021 \\
{School of Mathematics}, University of Edinburgh \\
\vspace{-0.5cm}

Visiting Assistant Professor / Lecturer  \hfill January 2012 - May 2015 \\
{Department of Statistical Science}, Duke University \\
\vspace{-0.5cm}

Postdoctoral Associate  \hfill July 2012 - April 2014 \\
{Department of Statistical Science}, Duke University \\
\vspace{-0.5cm}

Graduate Student Researcher \hfill September 2010 - December 2011 \\
{Novembre Lab}, UCLA \\
\vspace{-0.5cm}

Senior Statistical Consultant \hfill March 2009 - December 2011 \\
{Statistical Consulting Center}, UCLA \\
\vspace{-0.50cm}

Graduate Teaching Assistant \hfill September 2006 - July 2010 \\
{Dept. of Ecology and Evolutionary Biology, Dept. of Statistics}, UCLA \\

\vspace{3mm}

\section{\sc Teaching}


Duke University

\begin{list1}
\item[] Sta 30 - Statistics and Quantitative Literacy - \href{http://stat.duke.edu/courses/Spring12/sta10.1}{Fa 12}

\item[] Sta 102 - Introductory Biostatistics - \href{http://stat.duke.edu/courses/Spring13/sta102.001/}{Sp 13}, \href{https://stat.duke.edu/~cr173/Sta102_Sp14/}{Sp 14}, \href{https://stat.duke.edu/~cr173/Sta102_Fa14/}{Fa 14}, \href{https://stat.duke.edu/~cr173/Sta102_Sp15/}{Sp 15}, \href{https://stat.duke.edu/~cr173/Sta102_Fa15/}{Fa 15}, \href{http://stat.duke.edu/~cr173/Sta112_Sp16/}{Sp 16}, \href{http://stat.duke.edu/~cr173/Sta102_Su16/}{Su 16}

\item[] Sta 111 - Probability and Statistical Inference - \href{https://stat.duke.edu/~cr173/Sta111_Su14/}{Su 14}

\item[] Sta 112 - Better Living through Data Science - \href{http://stat.duke.edu/~cr173/Sta112_Fa16/}{Fa 16}

\item[] Sta 230 - Probability - \href{http://stat.duke.edu/courses/Spring12/sta104.1}{Fa 12}, \href{https://stat.duke.edu/~cr173/Sta230_Sp14/}{Sp 14}

\item[] Sta 323 - Statistical Computing - \href{http://stat.duke.edu/~cr173/Sta323_Sp16/}{Sp 16}, \href{http://stat.duke.edu/~cr173/Sta323_Sp17/}{Sp 17}, \href{http://stat.duke.edu/~cr173/Sta323_Sp18/}{Sp 18}, \href{http://stat.duke.edu/~cr173/Sta323_Sp19/}{Sp 19}

\item[] Sta 444 / 644 - Spatio-Temporal Modeling - \href{http://stat.duke.edu/~cr173/Sta444_Sp17/}{Sp 17}, \href{http://stat.duke.edu/~cr173/Sta444_Sp18/}{Sp 18}, \href{http://stat.duke.edu/~cr173/Sta444_Fa18/}{Fa 18}

\item[] Sta 523 - Statistical Programming - \href{https://stat.duke.edu/~cr173/Sta523_Fa14/}{Fa 14}, \href{https://stat.duke.edu/~cr173/Sta523_Fa15/}{Fa 15}, \href{https://stat.duke.edu/~cr173/Sta523_Fa16/}{Fa 16}, \href{https://stat.duke.edu/~cr173/Sta523_Fa17/}{Fa 17}, \href{https://stat.duke.edu/~cr173/Sta523_Fa18/}{Fa 18},
\href{https://sta523-fa21.github.io/}{Fa 21}

\item[] Sta 790 - Advanced Statistical Computing - \href{http://stat.duke.edu/~cr173/Sta790_Sp16/}{Sp 19}
\end{list1}

University of Edinburgh

\begin{list1}
\item[] Math 08068 - Facets of Mathematics - Regression Modeling Theme - Sp 19 

\item[] Math 11176 - Statistical Programming - \href{https://statprog-s1-2019.github.io/}{Sp 19}, \href{https://statprog-s1-2020.github.io/}{Sp 20}

\item[] Math 11205 - Machine Learning in Python - Fa 20, Fa 21
\end{list1}

\pagebreak


\section{\sc Online Teaching}

Coursera - \href{https://www.coursera.org/specializations/statistics}{Statistics with R Specialization}
\begin{list1}
\item[] \href{https://www.coursera.org/learn/bayesian}{Bayesian Statistics}
\item[] \href{https://www.coursera.org/learn/statistics-project}{Statistics with R Capstone}
\end{list1}

\section{\sc Publications}

Poulsen, J., Beirne, C., Rundel, C., Baldino, M., Kim, S., Knorr, J., Minich, T., Jin, L.,  Núñez, C., Xiao, S., Mbamy, W., Obiang, G., Masseloux, J., Nkoghe, T, Ebanega, M., Clark, C., Fay, M., Morkel, P., Okouyi, J., White, L., Wright, J. (2021). {\em Long distance seed dispersal by forest elephants}. Frontiers in Ecology And Evolution (in revision).

Çetinkaya-Rundel, M., Hardin, J., Baumer, B. S., McNamara, A., Horton, N. J., Rundel, C. (2021). {\em An educator's perspective of the tidyverse}. Technology Innovations in Statistics Education (in revision), arXiv preprint \href{https://arxiv.org/abs/2108.03510}{arXiv:2108.03510}.

\vspace{-0.15cm}
Beckman M., Çetinkaya-Rundel M., Horton N., Rundel C., Sullivan A., Tackett M. (2020) {\em Implementing Version Control With Git and GitHub as a Learning Objective in Statistics and Data Science Courses}. Journal of Statistics Education. 29 (Sup 1), 132 - 144. \href{https://doi.org/10.1080/10691898.2020.1848485}{DOI}.

\vspace{-0.15cm}
Johnson A., Rundel C., Hu J., Ross K., Rossman A. (2020) {\em Teaching an Undergraduate Course in Bayesian Statistics: A Panel Discussion}. Journal of Statistics Education. 28 (3), 251 - 261. \href{https://doi.org/10.1080/10691898.2020.1845499}{DOI}.


\vspace{-0.15cm}
Beirne C., Nuñez C., Baldino M., Kim S., Knorr J., Minich T., Jin L., Xiao S., Mbamy W., Obiang G., Masseloux J., Nkoghe T., Ebanega M., Rundel C., Wright J., Poulsen J. (2019) {\em Estimation of gut passage time of wild, free roaming forest elephants}. Wildlife Biology. 2019 (1).

\vspace{-0.15cm}
Cetinkaya-Rundel M., Rundel C.W. (2017) {\em Infrastructure and tools for teaching computing throughout the statistical curriculum}. The American Statistician. 72 (1), 58 - 65.

\vspace{-0.15cm}
Rundel C.W., Schliep E.M., Holland D., Gelfand A. (2015) {\em A data fusion approach for spatial analysis of speciated PM$_{2.5}$ across time}. Environmetrics. 26 (8), 515 - 525.

\vspace{-0.15cm}
Rundel C.W., Wunder M., Alvarado A.H., Ruegg K., Harrigan R., Schuh A., Jeffrey K., Siegel R., DeSante D.F., Smith T.B., Novembre J. (2013) {\em Novel statistical methods for integrating genetic and stable isotope data to infer individual-level migratory connectivity}. Molecular Ecology. 22 (16), 4163 - 4176.

\vspace{-0.15cm}
de Bocanegra H.T., Rostovsteva D., \c{C}etinkaya M., Rundel C.W., Lewis C. (2011). {\em Quality of reproductive health services to limited English proficient patients}. Journal of Health Care for the Poor and Underserved, 22 (4), 1167 - 1178.

\vspace{-0.15cm}
Walker D.W., Muffat J, Rundel C.W., Benzer S. (2006). {\em Overexpression of a Drosophila Homolog of Apolipoprotein D Leads to Increased Stress Resistance and Extended Lifespan}. Current Biology, 16 (7), 674 - 679.


\vspace{4mm}

%

\section{\sc Magazines}

Rundel, C.W., Cetinkaya-Rundel M. (2016) La Quinta is Spanish for next to Denny's, Chance 29 (2), 53 - 57


Rundel C.W. (2002) {\em Genes, Aging, and the Future of Longevity} Engineering \& Science, 65 (4), 36 - 40.

\vspace{4mm}

%

\section{\sc Talks \& Workshops}

RStudio Global 2021 \hfill January 2021
\begin{list1}
\item[] \href{https://www.rstudio.com/resources/rstudioglobal-2021/parsermd-parsing-r-markdown-for-fun-and-profit/}{parsermd - parsing R Markdown for fun and profit}
\end{list1}
\vspace{-3mm}

\href{https://sites.google.com/view/rssteachingstatisticssig/research-meetings/teaching-and-learning-of-maths-and-stats-computing-online}{TLMSCO} \hfill September 2020
\begin{list1}
\item[] Teaching computing using git and GitHub
\end{list1}
\vspace{-3mm}

\pagebreak

JSM 2020 (Invited) \hfill August 2020
\begin{list1}
\item[] Computation Infrastructure for Teaching Bayesian Modeling
\end{list1}
\vspace{-3mm}

\href{http://bit.ly/teach-r-online-mats}{Teaching Statistics and Data Science Online} (Online Workshop) \hfill July 2020
\begin{list1}
\item[] Workshop 1: Teaching R online with RStudio Cloud
\item[] Workshop 2: Building interactive tutorials in R
\item[] Workshop 3: Teaching computing with Git and GitHub
\end{list1} 
\vspace{-3mm}




RStudioConf 2020 \hfill January 2020
\begin{list1}
\item[] livecode: broadcast your live coding sessions from and to RStudio
\end{list1}
\vspace{-3mm}

JSM 2019 \hfill August 2019
\begin{list1}
\item[] ghclass: an R package for managing classes with GitHub
\end{list1}
\vspace{-3mm}

JSM 2019 (Workshop) \hfill July 2019
\begin{list1}
\item[] Reproducible Computing
\end{list1}
\vspace{-3mm}


UseR! 2019 \hfill July 2019
\begin{list1}
\item[] ghclass: an R package for managing classes with GitHub
\end{list1}
\vspace{-3mm}

SDSS 2019 (Invited) \hfill May 2019
\begin{list1}
\item[] Using Rocker containers and CI for teaching R-based courses
\end{list1}
\vspace{-3mm}

ICOTS10 2018 (Workshop) \hfill July 2018
\begin{list1}
\item[] \href{https://mine-cetinkaya-rundel.github.io/teach-data-sci-icots2018/}{Teaching Data Science, Reproducibly}
\end{list1}
\vspace{-3mm}

ISBA World Meeting 2018 (Short Course) \hfill June 2018
\begin{list1}
\item[] \href{https://mine-cetinkaya-rundel.github.io/repro-compute-isba18/}{Reproducible Computing}
\end{list1}
\vspace{-3mm}

Joint Statistical Meetings 2017 (Invited) \hfill August 2017
\begin{list1}
\item[] \href{https://github.com/rundel/Presentations/tree/master/JSM%202017}{Moving Away from Ad Hoc Statistical Computing Education}
\end{list1}
\vspace{-3mm}

UseR! 2017 (Tutorial) \hfill July 2017
\begin{list1}
\item[] \href{https://github.com/fmichonneau/2017-useR-reproducibility/}{Data Carpentry: Open and Reproducible Research with R}
\end{list1}
\vspace{-3mm}

Joint Statistical Meetings 2016 (Invited) \hfill August 2016
\begin{list1}
\item[] \href{https://github.com/rundel/Presentations/tree/master/JSM%202016}{Statistical Computing as an Introduction to Data Science}
\end{list1}
\vspace{-3mm}

UseR! 2016 \hfill July 2016
\begin{list1}
\item[] \href{https://github.com/rundel/Presentations/tree/master/UseR2016}{Continuous Integration and Teaching Statistical Computing with R}
\end{list1}
\vspace{-3mm}


Joint Statistical Meetings 2015 \hfill August 2015
\begin{list1}
\item[] \href{https://github.com/rundel/Presentations/tree/master/JSM%202015}{Teaching statistical computing leveraging the github ecosystem}
\end{list1}
\vspace{-3mm}

UseR! 2015 \hfill July 2015
\begin{list1}
\item[] \href{https://github.com/rundel/Presentations/tree/master/UseR2015}{Teaching R using the github ecosystem}
\end{list1}
\vspace{-3mm}


Data Analytics in Business and Social Science Seminar, Duke SSRI \hfill April 2015
\begin{list1}
\item[] \href{https://github.com/rundel/Presentations/tree/master/Duke%202015%20-%20DABSS}{Geospatial data and the R ecosystem}
\end{list1}
\vspace{-3mm}

Joint Statistical Meetings 2014 \hfill August 2014
\begin{list1}
\item[] \href{https://github.com/rundel/Presentations/tree/master/JSM%202014}{A Data Fusion Approach for Space-Time Analysis of Speciated PM$_{2.5}$}
\end{list1}
\vspace{-3mm}

Duke Dept of Statistical Science Seminar \hfill February 2014
\begin{list1}
\item[] \href{https://github.com/rundel/Presentations/tree/master/Duke%202014}{Using GPUs to improve the computational efficiency of Gaussian process models}
\end{list1}
\vspace{-3mm}


Joint Statistical Meetings 2013 \hfill August 2013
\begin{list1}
\item[] \href{https://github.com/rundel/Presentations/tree/master/JSM%202013}{GPUs, linear algebra, and efficient computing for Gaussian process models}
\end{list1}
\vspace{-3mm}

UseR! 2013 \hfill July 2013
\begin{list1}
\item[] \href{https://github.com/rundel/Presentations/tree/master/UseR2013}{Leveraging GPU libraries for efficient computation of Gaussian process models in R}
\end{list1}
\vspace{-3mm}

Joint Statistical Meetings 2012 \hfill August 2012
\begin{list1}
\item[] \href{https://github.com/rundel/Presentations/tree/master/JSM%202012}{Leveraging GPU Libraries for Efficient Computation of Bayesian Spatial Assignment Models in R}
\end{list1}
\vspace{-3mm}

UseR! 2012 \hfill June 2012
\begin{list1}
\item[] \href{https://github.com/rundel/Presentations/tree/master/UseR2012}{rgeos: spatial geometry predicates and topology operations in R}
\end{list1}
\vspace{-3mm}

Joint Statistical Meetings 2011 \hfill August 2011
\begin{list1}
\item[] \href{https://github.com/rundel/Presentations/tree/master/JSM%202011}{Spatial Models for Bird Origin Assignment Using Genetic and Isotopic Data}
\end{list1}
\vspace{-3mm}

\vspace{4mm}

\pagebreak

\section{\sc Service}

Guest Associate Editor, \href{https://www.tandfonline.com/action/journalInformation?show=aimsScope&journalCode=ujse20}{Journal of Statistics and Data Science Education} \hfill Fall 2021\\
Special Issue on Teaching Reproducibility and Responsible Workflow

DSS Master's Advisory Committee \hfill Fall 2017 - Spring 2019

\href{http://services.duke.edu/itac/}{Duke's Information Technology Advisory Council} \hfill Fall 2017 - present

DSS Computing Committee \hfill Summer 2014 - Spring 2019, Fall 2021 - present
\begin{list1}
\item[] Chair, Spring 2017 - Spring 2019, Fall 2021 - present              
\end{list1}

ASA DataFest @ Duke \hfill Fall 2011 - Spring 2019
\begin{list1}
\item[] Co-organizer
\end{list1}


Bayes Impact at Duke \hfill Fall 2014 - Spring 2016
\begin{list1}
\item[] Scientific Registry of Transplant Recipients
\item[] Motion Math
\end{list1}


\vspace{4mm}

\section{\sc \href{https://github.com/rundel/}{Software}}

\href{https://github.com/rundel/md4r}{\texttt{md4r}}: R wrapper of the md4c markdown parsing library.

\href{https://github.com/rundel/checklist}{\texttt{checklist}}: Tools for automating checking of R projects, with a focus on automated feedback via CI tooling like GitHub actions.

\href{https://github.com/rundel/parsermd}{\texttt{parsermd}}: Tools for parsing and programmatically interacting with R Markdown documents.

\href{https://github.com/rundel/learnrhash}{\texttt{learnrhash}}: Tools for recording student results for questions and exercises in learnr documents.

\href{https://github.com/rundel/livecode}{\texttt{livecode}}: Library for broadcasting source files during live codeing sessions.

\href{https://github.com/rundel/ghclass}{\texttt{ghclass}}: Library for managing classroom and assignment related tasks on github.

\href{https://github.com/rundel/rgeos}{\texttt{rgeos}}: R interface to the Geometry Engine, Open Source (GEOS) library.

\vspace{-0.15cm}
\href{https://github.com/rundel/isoscatR}{\texttt{isoscatR}}: R package for smoothed and continuous assignment testing (SCAT) of genetic samples

\vspace{-0.15cm}
\href{https://github.com/rundel/timezone}{\texttt{timezone}}: A small R package for finding timezone names from geographic coordinates

\vspace{-0.15cm}
\href{https://github.com/rundel/RcppGP}{\texttt{RcppGP}}: Tools for efficiently working with Gaussian Processes in R / C++

\vspace{-0.15cm}
\href{http://mapnik.org}{\texttt{mapnik}}: \href{https://github.com/rundel/carto-parser}{parser} and \href{https://github.com/rundel/carto-generator}{generator} for the \href{https://github.com/mapbox/carto}{carto} map style language.

\vspace{4mm}

\section{\sc Memberships}
American Statistical Association \\
International Society for Bayesian Analysis

\end{resume}
\end{document}




